Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.9)} \underline{Drafting Committee: DC90 (\today)}

### 2011-03-29 background_and_systematic.tex
Made changes to all sections.
The previous DC's mistakes have been corrected. The model descriptions are picked out in blue. A new section has been added to the summary.

The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state. \blue{The} recoiling proton is not detected \blue{and the calorimeter resolution does not allow}, separation of the latter events from rest of the data sample is not possible due to the experimental technique.
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation \blue{from} Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``Assoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform \blue{this} estimation is described in detail in
Ref.~\cite{Air08}.

>>>>

The data sample in the exclusive region contains events involving both production of real photons in which the proton remains intact and events involving the excitation of the target proton to a $\Delta^+$ resonant state. \blue{The} recoiling proton is not detected \blue{and the calorimeter resolution does not allow}, separation of the latter events from rest of the data sample.
No systematic uncertainty is assigned for the contribution from these events; they are treated as part of the signal. A Monte Carlo calculation based on the parameterisation \blue{from} Ref.~\cite{Bra76} is used to estimate the contribution to the event sample from resonant production in each kinematic bin. The results, denoted associated fraction and labelled ``Assoc. fraction'', are shown in the last row of each figure in the results section. The method used to perform \blue{this} estimation is described in detail in
Ref.~\cite{Air08}.

### 2011-03-29 experiment_and_data.tex
Made changes to all sections.
The previous DC's mistakes have been corrected. The model descriptions are picked out in blue. A new section has been added to the summary.

An event sample was selected using a missing-mass technique requiring that the squared missing-mass $M_{\textrm{X}}^{2}=(q+\blue{P}-q')^{2}$ of the \blue{$e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$} measurement corresponded to the square of the proton mass within the limits of the energy resolution of the calorimeter. Here, $q$ is the four-momentum of the virtual photon, $\blue{P}$ is the \blue{initial} four-momentum of the target proton and $q'$ is the four\blue{-}momentum of the produced photon. The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}. This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 data set \cite{Bur10}.

>>>>

An event sample was selected using a missing-mass technique requiring
that the squared missing-mass $M_{\textrm{X}}^{2}=(q+\blue{P}-q')^{2}$
of the \blue{$e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$} measurement
corresponded to the square of the proton mass within the limits of the
energy resolution of the \blue{H{\sc ermes}} calorimeter. Here, $q$ is the four-momentum of the virtual photon, $p$ is the \blue{initial} four-momentum of the target proton and $q'$ is the four\blue{-}momentum of the produced photon. The ``exclusive region'' was defined as ($-1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in Ref.~\cite{Air09}. This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 data set \cite{Bur10}.

### 2011-03-29 frame.tex
Made changes to all sections.
The previous DC's mistakes have been corrected. The model descriptions are picked out in blue. A new section has been added to the summary.

\documentclass{elsart}
\usepackage[pdftex]{hyperref}
\usepackage{amstext,amsmath,amsfonts,amssymb}
\usepackage{bm}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage{vruler}
\usepackage{color}
\usepackage{subfigure}
\usepackage{mathrsfs}
\usepackage{eufrak}
\usepackage{float}
\usepackage{rotating}
\textwidth 17.0cm
\oddsidemargin 0.0cm
\evensidemargin 0.0cm
\topmargin 0.5cm
% ===========================================================================

@@

\title{
	Beam-Helicity and Charge Asymmetries \\
        in the Bethe-Heitler and DVCS processes on \\
        an Unpolarised Proton Target
  	\underline{Paper Tag: PDVCS (v0.8)}
        \underline{Drafting Committee: DC90 (\today)}
}

\collab{HERMES Collaboration}
\begin{abstract}
Beam-helicity and charge asymmetries in the hard exclusive leptoproduction of
real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the \blue{H{\sc ermes}} data set of 2006-2007 using a
missing-mass event selection technique. The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from an earlier data set of 1996-2005 previously analysed in the same manner by the collaboration. Results from \blue{the two} data sets are found to be compatible with each other. Combined results from these data sets are extracted and \blue{represent} the statistically most precise asymmetry amplitude measurements available in the \blue{H{\sc ermes}} kinematic region.
\end{abstract}

>>>>

\documentclass{elsart}
\usepackage[pdftex]{hyperref}
\usepackage{amstext,amsmath,amsfonts,amssymb}
\usepackage{bm}
\usepackage{lscape}
\usepackage{graphicx}
\usepackage{vruler}
\usepackage{color}
\usepackage{subfigure}
\usepackage{mathrsfs}
\usepackage{eufrak}
\usepackage{float}
%\usepackage{superscriptaddress}
\usepackage{rotating}
\textwidth 17.0cm
\oddsidemargin 0.0cm
\evensidemargin 0.0cm
\topmargin 0.5cm
% ===========================================================================

@@

\title{
	Beam-Helicity and Charge Asymmetries \\
        in the Bethe-Heitler and DVCS processes on \\
        an Unpolarised Proton Target
  	\underline{Paper Tag: PDVCS (v0.9)}
        \underline{Drafting Committee: DC90 (\today)}
}

% List of Institute Addresses 
\collab{HERMES Collaboration}
\begin{abstract}
Beam-helicity and charge asymmetries in the hard exclusive leptoproduction of
real photons from an unpolarised proton target by a 27.6\,GeV lepton beam 
are extracted from the \blue{H{\sc ermes}} data set of 2006-2007 using a
missing-mass event selection technique. The beam-charge asymmetry amplitudes extracted from the new data set are statistically more precise than those extracted from \blue{the} earlier data set of 1996-2005 previously analysed in the same manner by the collaboration. Results from \blue{the two} data sets are found to be compatible with each other. Combined results from these data sets are extracted and \blue{represent} the statistically most precise asymmetry amplitude measurements available in the \blue{H{\sc ermes}} kinematic region.
\end{abstract}

### 2011-03-29 results.tex
Made changes to all sections.
The previous DC's mistakes have been corrected. The model descriptions are picked out in blue. A new section has been added to the summary.

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, \blue{is} shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish in this $-t$ region due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude is compatible with zero, as is the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude, which is dependent on the squared DVCS term. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude are shown in the second row of Fig.~\ref{bsa_xbjrange}. Neither the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.

@@

The dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations made from a hybrid quark-diquark model with a Regge term that is included to accurately describe parton distribution functions at low $x$ values. The model incorporates fits only to global deep inelastic scattering and elastic data (for the limits and moments of the underlying GPDs) and exclusive data from Jefferson Lab (to describe the skewness dependence). The model is trained in the kinematic domain of the Hall A and B experiments at Jefferson Lab and the extracted underlying physics quantities are used to calculate the asymmetries in the H{\sc ermes} kinematic region. The model fails to describe the presented data; the predictions have consistently smaller magnitudes than the amplitudes presented in this work.

The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted in the VGG formalism from experimental data (including the H{\sc ermes} data from 1996-2005). The extraction of the Compton Form Factors is nearly model independent, but cannot be extended byond the H{\sc ermes} kinematic domain. The presented data is well described by the calculations.

In order to provide more detailed information \blue{that can be used in} future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. There is no observed $-t$ depend\blue{ence} on any of the \blue{$\mathcal{A}_{\textrm{LU}}$} amplitudes in either of the distinct ranges of $x_{\textrm{B}}$. Also no additional features or $-t$ dependenc\blue{es} are observed for the \blue{$\mathcal{A}_{\textrm{C}}$} amplitudes in these separate $x_{\textrm{B}}$ ranges.

>>>>

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish in this $-t$ region due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude is compatible with zero, as is the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude, which is dependent on the squared DVCS term. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude are shown in the second row of Fig.~\ref{bsa_xbjrange}. Neither the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.

@@

\blue{The dotted curve in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} shows the result of a calculation made from a hybrid quark-diquark model with a Regge term that is included in order to describe accurately parton distribution functions at low $x$ values. The model incorporates fits only to global deep inelastic scattering and elastic data (for the limits and moments of the underlying GPDs) and exclusive data from Jefferson Lab (to describe the skewness dependence). The model is trained in the kinematic domain of the Hall A and B experiments at Jefferson Lab and the extracted underlying physics quantities are used to calculate the asymmetries in the H{\sc ermes} kinematic region. The model fails to describe the presented data; the predictions have consistently smaller magnitudes than the amplitudes presented in this work.

The open crosses in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations of the asymmetries using Compton Form Factors extracted in the VGG formalism from experimental data (including the H{\sc ermes} data from 1996-2005). The extraction of the Compton Form Factors is nearly model independent, but cannot be extended byond the H{\sc ermes} kinematic domain. The presented data is well described by the calculations.}

In order to provide more detailed information \blue{that can be used in} future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. There is no observed $-t$ depend\blue{ence} on any of the \blue{$\mathcal{A}_{\textrm{LU}}$} amplitudes in either of the distinct ranges of $x_{\textrm{B}}$. No additional features or $-t$ dependenc\blue{es} are observed for the \blue{$\mathcal{A}_{\textrm{C}}$} amplitudes in these separate $x_{\textrm{B}}$ ranges.

### 2011-03-29 summary.tex
Made changes to all sections.
The previous DC's mistakes have been corrected. The model descriptions are picked out in blue. A new section has been added to the summary.

Beam\blue{-}helicity and beam\blue{-}charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}. \blue{An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained 1996-2005 experimental period \blue{described in} Ref.~\cite{Air09}}. A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. The resulting beam\blue{-}charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam\blue{-}helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic\blue{s} of the beam\blue{-}charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are compared to calculations from ongoing work to fit GPD models to experimental data. \blue{This model fit~\cite{Kum09}} includes the H{\sc ermes} data set from 1996-2005 \blue{shown in} Ref.~\cite{Air09}. The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes. All amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$. No localised features are observed in any particular $t$-bin.

>>>>

Beam\blue{-}helicity and beam\blue{-}charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}. \blue{An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}}. A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and \blue{the }asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. The resulting beam\blue{-}charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam\blue{-}helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonic\blue{s} of the beam\blue{-}charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are compared to calculations from ongoing work to fit GPD models to experimental data. \blue{One} model fit~\cite{Kum09} includes the H{\sc ermes} data set from 1996-2005 \blue{shown in} Ref.~\cite{Air09}. The model achieves good agreement with the presented beam-helicity asymmetry amplitude results, and fair agreement with the beam-charge asymmetry amplitudes. \blue{The other model fit does not include the H{\sc ermes} data from 1996-2005 and fails to describe the presented data accurately. A third set of calculations is presented that arise from efforts to extract the Compton Form Factors from experimental data at discrete kinematic points. The fit on which these calculations are based includes the H{\sc ermes} data set from 1996-2005. The calculations describe the data well, but cannot be extrapolated past the H{\sc ermes} kinematic domain.} All \blue{data} amplitudes are also presented \blue{as projections} in $-t$ in bins of $x_{\textrm{B}}$. No localised features are observed in any particular $t$-bin.

### 2011-03-29 theory.tex
Made changes to all sections.
The previous DC's mistakes have been corrected. The model descriptions are picked out in blue. A new section has been added to the summary.

Generalised parton distributions depend upon four kinematic variables: the
Mandelstam variable $t=(\blue{P-P^{\prime}})^2$, which is the squared momentum
transfer to the target nucleon in the scattering process with \blue{$P$ ($P^{\prime}$})
representing the initial (final) four-momentum of the proton; the average
fraction $x$ of the nucleon's longitudinal momentum carried by the active
quark throughout the scattering process; half the difference in the
change of the fraction of the nucleon's longitudinal momentum carried by the
active quark at the start and end of the process, written as the skewness
variable $\xi$; and the square $-Q^2=q^2$ of the four-momentum of the virtual photon that mediates the lepton-proton scattering process. In the Bjorken limit of $Q^2\rightarrow\infty$ with
fixed $t$, $\xi$ is related to the Bjorken variable
$x_{\textrm{B}}=\frac{-q^2}{2\blue{P}.q}$ as
$\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
against $x_{\textrm{B}}$ because there is no consensus on an experimentally
observable representation of $\xi$.

@@

The differential four-fold cross section for the leptoproduction of real photons
from an unpolarised target can be written \cite{Bel02b}
\begin{center}
\begin{equation}
\frac{\textrm{d}^4\sigma}{\textrm{d}x_{\textrm{B}}\textrm{d}Q^{2}\textrm{d}
|t|\textrm{d}\phi} =
\frac{x_{\textrm{B}}e^{6}}{32(2\pi)^{4} Q^{4}\sqrt{1+\epsilon^{2}}}
|\tau|^{2},
\end{equation}
\end{center}
where $e$ is the elementary
charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
the nucleon mass and $\phi$ is the
azimuthal angle between the scattering and production planes \cite{Tre04}.
The scattering amplitude $\tau$ can be written
\begin{center}
\begin{equation}
|\tau|^{2} = |\tau_{\textrm{BH}}|^{2} +
|\tau_{\textrm{DVCS}}|^{2} + \textrm{I},
\end{equation}
\end{center}
with contributions from the \textrm{BH} process ($\tau_{\textrm{\textrm{BH}}}$),
the DVCS process
($\tau_{\textrm{DVCS}}$) and the interference term (I). These
contributions can be written 
\begin{equation}
 |\tau_{\textrm{BH}}|^{2} =
\frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\left(c_{0}^{
\textrm{BH}} + \sum_{n=1}^2 c_{n}^{\textrm{BH}}\cos(n\phi)\right),
\label{e:tbh}
\end{equation}
\begin{equation}
 \hspace{2.2cm}|\tau_{\textrm{DVCS}}|^{2} =
K_{\textrm{DVCS}}\left(c_{0}^{\textrm{DVCS}} +
\sum_{n=1}^2
c_{n}^{\textrm{DVCS}}\cos(n\phi) + \lambda
s_{1}^{\textrm{DVCS}}\sin\phi\right),
\label{e:tdvcs}
\end{equation}
\begin{equation}
\hspace{3.7cm} \textrm{I} = \frac{- e_\ell
K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{0}^{\textrm{
I}}
+
\sum_{n=1}^3 c_{n}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
s_{n}^{\textrm{I}}\sin(n\phi)\right),
\label{e:ti}
\end{equation}
where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
of the BH process and $\lambda$ and $e_\ell$ are respectively the
helicity and unit charge of the lepton beam.  The
quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
$K_{\textrm{DVCS}}=1/Q^2$
and $K_{\textrm{I}}=1/(x_{\textrm{B}}yt)$ are kinematic factors, where
$y$ is the fraction of the beam energy carried by the virtual photon in
the target rest frame. A full
explanation of the Fourier coefficients [$c_n^V,s_n^W$]
($V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$) can be
found in
Ref.~\cite{Bel02b}.

@@

\begin{align}
\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) -
(\textrm{d}\sigma(\phi)^{+\leftarrow} + 
\textrm{d}\sigma(\phi)^{-\leftarrow})}
{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) +
(\textrm{d}\sigma(\phi)^{+\leftarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&  \nonumber \\
&=\dfrac{K_{\textrm{DVCS}}
s_{1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)},&
\label{e:aludvcs}
\end{align}

\begin{align}
\hspace{0.5cm}\mathcal{A}_{\textrm{C}}(\phi) &\equiv  
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{+\leftarrow}) -
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
+
\textrm{d}\sigma(\phi)^{+\leftarrow}) +
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&    \nonumber \\
&=\dfrac{{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=0}^3
c_{n}^{\textrm{I}}\cos(n\phi)}}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_
{2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)} ,&
\label{e:ac}
\end{align}
where $\textrm{d}\sigma(\phi)^+$ ($\textrm{d}\sigma(\phi)^-$) refers to
cross sections with positive (negative) beam charge and
$\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer
to cross sections taken with beam spin parallel \blue{(anti-parallel)} with the
beam momentum.

This paper provides a set of results analogous to those reported in
Ref.~\cite{Air09}. The analysis presented here additionally includes a larger, independent data set taken during the years 2006 and 2007 after the experiment was upgraded in the target region. 
The results in this paper do not make use of any of the information from the
upgraded detector equipment (i.e. a missing-mass technique for event selection is used), but represent the largest DVCS data set that will
be published by H{\sc ermes}.

>>>>

Generalised parton distributions depend upon four kinematic variables: the
Mandelstam variable $t=(p-p^{\prime})^2$, which is the squared momentum
transfer to the target nucleon in the scattering process with $p$ ($p^{\prime}$)
representing the initial (final) four-momentum of the proton; the average
fraction $x$ of the nucleon's longitudinal momentum carried by the active
quark throughout the scattering process; half the difference in the
change of the fraction of the nucleon's longitudinal momentum carried by the
active quark at the start and end of the process, written as the skewness
variable $\xi$; and the square $-Q^2=q^2$ of the four-momentum of the virtual photon that mediates the lepton-proton scattering process. In the Bjorken limit of $Q^2\rightarrow\infty$ with
fixed $t$, $\xi$ is related to the Bjorken variable
$x_{\textrm{B}}=\frac{-q^2}{2p\cdot q}$ as
$\xi\approx\frac{x_\textrm{B}}{2-x_\textrm{B}}$. The results are presented
against $x_{\textrm{B}}$ because there is no consensus on an experimentally
observable representation of $\xi$.

@@

The differential four-fold cross section for the leptoproduction of real photons
from an unpolarised target can be written \cite{Bel02b}
\begin{center}
\begin{equation}
\frac{\textrm{d}^4\sigma}{\textrm{d}x_{\textrm{B}}\textrm{d}Q^{2}\textrm{d}
|t|\textrm{d}\phi} =
\frac{x_{\textrm{B}}e^{6}}{32(2\pi)^{4} Q^{4}\sqrt{1+\epsilon^{2}}}
|\tau|^{2},
\end{equation}
\end{center}
where $e$ is the elementary
charge, $\epsilon=2x_\textrm{B}\frac{M}{Q}$ with $M$
the nucleon mass\blue{,} and $\phi$ is the
azimuthal angle between the scattering and production planes \cite{Tre04}.
The scattering amplitude $\tau$ can be written
\begin{center}
\begin{equation}
|\tau|^{2} = |\tau_{\textrm{BH}}|^{2} +
|\tau_{\textrm{DVCS}}|^{2} + \textrm{I},
\end{equation}
\end{center}
with contributions from the \textrm{BH} process ($\tau_{\textrm{\textrm{BH}}}$),
the DVCS process
($\tau_{\textrm{DVCS}}$) and the interference term (I). These
contributions can be written 
\begin{equation}
 |\tau_{\textrm{BH}}|^{2} =
\frac{K_{\textrm{BH}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\left(c_{0}^{
\textrm{BH}} + \sum_{n=1}^2 c_{n}^{\textrm{BH}}\cos(n\phi)\right),
\label{e:tbh}
\end{equation}
\begin{equation}
 \hspace{2.2cm}|\tau_{\textrm{DVCS}}|^{2} =
K_{\textrm{DVCS}}\left(c_{0}^{\textrm{DVCS}} +
\sum_{n=1}^2
c_{n}^{\textrm{DVCS}}\cos(n\phi) + \lambda
s_{1}^{\textrm{DVCS}}\sin\phi\right),
\label{e:tdvcs}
\end{equation}
\begin{equation}
\hspace{3.7cm} \textrm{I} = \frac{- e_\ell
K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}\left(c_{0}^{\textrm{
I}}
+
\sum_{n=1}^3 c_{n}^{\textrm{I}}\cos(n\phi) + \lambda \sum_{n=1}^2
s_{n}^{\textrm{I}}\sin(n\phi)\right),
\label{e:ti}
\end{equation}
where $\mathcal{P}_1(\phi)$ and $\mathcal{P}_2(\phi)$ are the lepton propagators
of the BH process and $\lambda$ and $e_\ell$ are respectively the
helicity and unit charge of the lepton beam.  The
quantities $K_{\textrm{BH}}=1/(x_\textrm{B}^2t(1+\epsilon^2)^2)$,
$K_{\textrm{DVCS}}=1/Q^2$
and $K_{\textrm{I}}=1/(x_{\textrm{B}}yt)$ are kinematic factors, where
$y$ is the fraction of the beam energy carried by the virtual photon in
the target rest frame. A full
explanation of the Fourier coefficients [$c_n^V,s_n^W$]
($V\in[\textrm{BH,DVCS},\textrm{I}]$ and $W\in[\textrm{DVCS},\textrm{I}]$) can be
found in
Ref.~\cite{Bel02b}.

@@

\begin{align}
\mathcal{A}^{\textrm{DVCS}}_{\textrm{LU}}(\phi) &\equiv
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) -
(\textrm{d}\sigma(\phi)^{+\leftarrow} + 
\textrm{d}\sigma(\phi)^{-\leftarrow})}
{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{-\rightarrow}) +
(\textrm{d}\sigma(\phi)^{+\leftarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&  \nonumber \\
&=\dfrac{K_{\textrm{DVCS}}
s_{1}^{\textrm{DVCS}}\sin\phi}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{DVCS}}\cos(n\phi)} \blue{\textrm{\,\,and}}&
\label{e:aludvcs}
\end{align}

\begin{align}
\hspace{0.5cm}\mathcal{A}_{\textrm{C}}(\phi) &\equiv  
\frac{(\textrm{d}\sigma(\phi)^{+\rightarrow} +
\textrm{d}\sigma(\phi)^{+\leftarrow}) -
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}{(\textrm{d}\sigma(\phi)^{+\rightarrow}
+
\textrm{d}\sigma(\phi)^{+\leftarrow}) +
(\textrm{d}\sigma(\phi)^{-\rightarrow}
+ \textrm{d}\sigma(\phi)^{-\leftarrow})}&    \nonumber \\
&=\dfrac{{-\dfrac{K_{\textrm{I}}}{\mathcal{P}_{1}(\phi)\mathcal{P}_{2}(\phi)}
\displaystyle\sum_{n=0}^3
c_{n}^{\textrm{I}}\cos(n\phi)}}{\dfrac{K_{\textrm{BH}}}{\mathcal{P}_{1}
(\phi)\mathcal{P}_
{2}(\phi)}
\displaystyle\sum_{n=0}^2
c_{n}^{\textrm{BH}}\cos(n\phi) + 
K_{\textrm{DVCS}}\displaystyle\sum_{n=0}^2 c_{n}^{\textrm{DVCS}}\cos(n\phi)} ,&
\label{e:ac}
\end{align}
where $\textrm{d}\sigma(\phi)^+$ ($\textrm{d}\sigma(\phi)^-$) refers to
cross sections with positive (negative) beam charge and
$\textrm{d}\sigma(\phi)^\rightarrow$ ($\textrm{d}\sigma(\phi)^\leftarrow$) refer
to cross sections taken with beam spin parallel \blue{(anti-parallel)} \blue{to} the
beam momentum.

The analysis presented here additionally includes a larger,
independent data set taken during the years 2006 and 2007 after the
experiment was upgraded in the target region. The results in this paper do not make use of any of the information from the
upgraded detector equipment (i.e. a missing-mass technique for event selection is used), but represent the largest DVCS data set that will
be published by H{\sc ermes}.
